THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY.

### 2016-09-13 DishReflectometry/Paper1_v3.tex
Tweaks to abstract

\begin{abstract}
Spectral structure from instrumental systematics is the current
limiting factor for the experiments attempting to detect the redshifted 21~cm
signal from the Epoch of Reionization (EoR). 
Recent advances in the delay spectrum methodology for measuring the
21~cm EoR power spectrum have brought new attention to the impact that
the frequency performance of antenna elements has on the viability of
making this challenging measurement.
%Systematics are specific to
%instruments and their direct measurement or estimation is not always
%straightforward. 
%The Hydrogen Epoch of Reionization Array (HERA) uses the delay
%spectrum technique for estimating of 21~cm power spectrum. 
In particular, the delay spectrum formalism provides a relationship
between time-domain reflectrometry profiles that can be directly
measured with a vector network analyzer (VNA) and the power spectrum modes accessible
to a 21~cm EoR experiment.
%In a unique way, the
%delay spectrum technique directly translates to reflectometry in case of
%measuring instrumental response and allows the direct measurement of systematic
%effects in individual array element.  
In this paper, we derive the explicit relationship between $S_{11}$ measurements
made by a VNA and the corresponding convolving kernel in delay space.
Using this formalism, we examine
the spectral chromaticity of the prototype antenna elements that
constitute Hydrogen Epoch of Reionization Array (HERA) 
between 100 and 200~MHz.
These reflectometry measurements exhibit spurious chromatic structure relative
to electromagnetic simulations, but we find 
that even without compensating for this structure, the antenna element
will support measuring $k$ modes with line-of-sight components 
$k_{\parallel} >0.2 h~Mpc^{-1}$.  
%The performance is significantly better at the high frequency subbands of observation. 
When combined with the powerful foreground weighting methods used in optimal
quadratic estimation,
HERA should be capable of measuring the
power spectrum at $k_{\parallel} > 0.1$. This study
qualifies HERA as a power spectrum instrument and serves as an
important method for designing and measuring instrumental systematics for any future
experiment aiming to detect the 21~cm EoR power spectrum.  
\end{abstract}

>>>>

\begin{abstract}
Spectral structure from instrumental systematics is the current
limiting factor for the experiments attempting to detect the redshifted 21~cm
signal from the Epoch of Reionization (EoR). 
Recent advances in the delay spectrum methodology for measuring the
21~cm EoR power spectrum have brought new attention to the impact that
an antenna's frequency performance has on the viability of
making this challenging measurement.
%Systematics are specific to
%instruments and their direct measurement or estimation is not always
%straightforward. 
%The Hydrogen Epoch of Reionization Array (HERA) uses the delay
%spectrum technique for estimating of 21~cm power spectrum. 
In particular, it provides straightforward relationship
between time-domain reflectrometry profiles that can be directly
measured with a vector network analyzer (VNA) and the power spectrum modes accessible
to a 21~cm EoR experiment.
%In a unique way, the
%delay spectrum technique directly translates to reflectometry in case of
%measuring instrumental response and allows the direct measurement of systematic
%effects in individual array element.  
In this paper, we derive the explicit relationship between $S_{11}$ measurements
made by a VNA and the extent of sidelobes of bright foregrounds in delay space.
Using this formalism, we examine
the spectral chromaticity of the prototype antenna elements that
constitute Hydrogen Epoch of Reionization Array (HERA) 
between 100 and 200~MHz.
These reflectometry measurements exhibit spurious structure relative
to electromagnetic simulations, but we find 
that even without compensating for this structure, the antenna element
will support measuring $k$ modes with line-of-sight components of
$k_{\parallel} >0.2 h~Mpc^{-1}$.  
%The performance is significantly better at the high frequency subbands of observation. 
We also find that when combined with the powerful foreground weighting methods used in optimal
quadratic estimation,
HERA should be capable of measuring the
power spectrum at $k_{\parallel} > 0.1$. This study represents a major step toward
qualifying HERA as a power spectrum instrument and highlights as an
important method for characterizing instrumental systematics for future
experiments aiming to detect the 21~cm EoR power spectrum.  
\end{abstract}
